---
title: "PA1_template"
author: "Jaymes Pyne"
date: "10/27/2020"
output: md_document
---
# Reproducible Research: Week 2 Assignment (PA1_Template)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup Code

```{r steps, echo=T} 
library(ggplot2)
library(plyr)

setwd('C:\\Users\\Jaymes Pyne\\Google Drive\\1_Stanford_Pyne\\Classes\\Coursera\\Data_Science_Specialization\\5 Reproducible Research')

  steps<-read.csv('./2_Data/activity.csv',header=T)
  stepsc<-steps[!is.na(steps),]
  steps$date<-as.Date(steps$date,"%Y-%m-%d")
```

## Histogram of Number of Steps Taken Each Day (Missing Values Removed)
```{r,echo=T}
  stepspd<-aggregate(x=steps[c("steps")],by=list(date=steps$date),
                     na.rm=T,FUN=sum,nfrequency=1)
  hist(stepspd$steps,xlab="Steps",main="Total Steps Per Day")
```

## Summary Statistics of Steps Taken Per Day (MIssing Values Removed)

```{r stepspd, echo=T}
summary(stepspd$steps)
```

## Average Daily Activity Pattern (Missing Values Removed)

```{r, echo=T}
stepsap<-aggregate(x=steps[c("steps")],by=list(interval=steps$interval),na.rm=T,mean)
ggplot(stepsap, aes(interval,steps))+
	 geom_line()+
	 labs(x="Interval",y="Average Steps Taken",title="Average Steps Per Interval Across All Days")+
	 theme_bw()
```

Interval 835 has the most number of steps on average across days.

# With Imputed Missing Values

## First, count all the NAs in the dataset

```{r,echo=T}
sapply(steps,function(x) sum(is.na(x)))
```

## Next, impute missing values with the mean by interval

```{r,echo=T}
imputem<-function(x) replace(x,is.na(x),mean(x,na.rm=T))
steps2<-ddply(steps,~interval,transform,steps=imputem(steps))
```

## Histogram of total steps taken per day (Imputed Missing Values)
```{r,echo=T}
stepspd2<-aggregate(x=steps2[c("steps")],by=list(date=steps2$date),na.rm=T,FUN=sum,nfrequency=1)
hist(stepspd2$steps,xlab="Steps",main="Total Steps Per Day (Mean-Imputed NAs)")
```

### Compared to listwise deletion of NAs
```{r,echo=T}
hist(stepspd$steps,xlab="Steps",main="Total Steps Per Day (Mean-Imputed NAs)")
```

## Summary statistics of steps taken per day (mean-imputed NAs)

```{r,echo=T}
summary(stepspd2$steps)
```

### Compared to listwise deletion of NAs

```{r,echo=T}
summary(stepspd$steps)
```

#Weekdays vs. Weekends

##Plot of Number of Steps Taken in Weekdays and Weekend	

```{r,echo=T}
steps2$dow<-weekdays(as.Date(steps2$date))
steps2$wknd<-factor(steps2$dow,
			levels=c("Monday","Tuesday","Wednesday",
				   "Thursday","Friday","Saturday","Sunday"),
			labels=c("Weekday","Weekday","Weekday",
				   "Weekday","Weekday","Weekend","Weekend"))

stepsap2<-aggregate(x=steps2[c("steps")],by=list(interval=steps$interval,wknd=steps2$wknd),na.rm=T,mean)
ggplot(stepsap2, aes(interval,steps))+
	 geom_line()+
	 labs(x="Interval",y="Average Steps Taken",title="Average Steps Per Interval By Weekdays and Weekends")+
	 facet_grid(.~wknd) + facet_grid(rows=vars(wknd))+
	 theme_bw()
```












